\begin{thebibliography}{00}
    \bibitem{b2} V. Chau, X. Chu, H. Liu, and Y.-W. Leung,
``Energy Efficient Job Scheduling with DVFS for CPU-GPU Heterogeneous Systems,'' in \textit{Proceedings of the Eighth International Conference on Future Energy Systems},
in e-Energy ’17.
\bibitem{b3} J. Choquette, W. Gandhi, O. Giroux, N. Stam, and R. Krashinsky, ``NVIDIA A100 Tensor Core GPU: Performance and Innovation,'' IEEE Micro, vol. 41, no. 2, pp. 29–35, Mar. 2021, doi: \href{https://doi.org/10.1109/mm.2021.3061394}{https://doi.org/10.1109/mm.2021.3061394}.
\bibitem{b6} ``Introduction to cloud TPU  |  Google Cloud,'' Google, \href{https://cloud.google.com/tpu/docs/intro-to-tpu} (accessed Apr. 7, 2024).
\bibitem{b5} R. Krashinsky, O. Giroux, S. Jones, N. Stam, and S. Ramaswamy, ``NVIDIA Ampere Architecture In-Depth,'' NVIDIA Technical Blog, May 14, 2020. \href{https://developer.nvidia.com/blog/nvidia-ampere-architecture-in-depth/}{https://doi.org/10.1109/mm.2021.3061394}
    \bibitem{b7} N. P. Jouppi et al., TPU v4: An Optically Reconfigurable Supercomputer for Machine Learning with Hardware Support for Embeddings. 2023.
\bibitem{b4} ``NVIDIA Tesla P100.'' Available: \href{https://images.nvidia.com/content/pdf/tesla/whitepaper/pascal-architecture-whitepaper.pdf}{https://images.nvidia.com/pascal-architecture-whitepaper.pdf}
\bibitem{b8} Y. Wang \textit{et al.}, “Benchmarking the Performance and Energy Efficiency of AI Accelerators for AI Training.” arXiv, Oct. 08, 2020. doi: \href{https://doi.org/10.48550/arXiv.1909.06842}{10.48550/arXiv.1909.06842}.
\end{thebibliography}